\chapter{Conclusion and future work}
\label{ch:Conclusion}

The proposed framework has demonstrated the capability of detecting anomalies in generic time domain data. The proposed modular structure is a key for enabling the framework to be considered a prototype that can be applied to a wide range of applications. The unsupervised learning approach further eases and accelerates the adaptation of this solution into different domains. 

The deployment of the solution also for \gls{glo:edge} enables the framework to expand the range of applicability beyond classical industrial environments, toward non-standard applications. The intrinsic cybersecurity of edge devices is a nice byproduct that can be exploited whenever the framework is deployed in a critical infrastructure.

In future work, there is significant potential for further testing and refinement of the already developed framework. One path to explore involves testing the edge implementation on a degrading system rather than relying on simulated degradation through environmental parameter changes. This approach could provide invaluable insights into the robustness and adaptability of the framework in critical scenarios. Additionally, deploying the remaining algorithms within the edge framework to address the limitations of K-means \gls{glo:clust}ing presents an exciting opportunity. Since the repertoire of algorithms shown promising results on real word datasets, deploying all of them also in the edge version of the framework allows to offer a more comprehensive solution to complex problems in \gls{glo:edge} environments.

The framework could also be enhanced from the user experience perspective by developing a Graphical User Interface (\gls{gui}) that allows to interact with the framework in a more intuitive way. The already developed \gls{cli} could remain a secondary option for advanced users, or be used in the background by the \gls{gui} to execute the framework's functionalities. 