% for glossary entry
% @entry{bird,
%     name={bird},
%     description = {feathered animal},
%     see={[see also]{duck,goose}}
% }

% if this bib file does not work, try using \input{file.tex}
% where all the \newabbreviation commands have been inserted
% containing all the definitions

% Gls to capitalize first letter
% GLS for full uppercase
% for abbreviations also
% glsxtrshort for abbreviation
% similar for long, full, and capital configurations, add pl at the end for plurals
% glsentryshort, long, plural (referred to shorts) must be used when in section titles
% glslink to allow the link but use a different text (as for href)


% if you want to use also description for the abbreviations/acronyms, you should use bib2gls and define all the entries in a bib file, which is incompatible with Overleaf

\newacronym{pm}{PM}{Proactive Maintenance} %% maintenance techniques
\newacronym{pvm}{PvM}{Preventive Maintenance}
\newacronym{rm}{RM}{Reactive Maintenance}
\newacronym{pdm}{PdM}{Predictive Maintenance}
\newacronym{cbm}{CBM}{Condition Based Maintenance}
\newacronym{iot}{IOT}{Internet Of Things}
\newacronym{os}{OS}{Operating System}
\newacronym{rul}{RUL}{\gls{glo:rul}}


\newacronym{nd}{ND}{Novelty Detection}  %% machine learning
\newacronym{fd}{FD}{Fault Detection}    
\newacronym{ml}{ML}{Machine Learining}  
\newacronym{uml}{UML}{Unsupervised Machine Learining}
\newacronym{svm}{SVM}{Support Vector Machine}
\newacronym{nu_svm}{$\nu$-SVM}{One Class \gls{svm}}
\newacronym{iforest}{iForest}{Isolation Forest}
\newacronym{mlp}{MLP}{Multilayered Perceptront}
\newacronym{dl}{DL}{\gls{glo:deep}}
\newacronym{ann}{ANN}{Artificial Neural Network}
\newacronym{dt}{DT}{Decision Tree}
\newacronym{knn}{$k$-NN}{k-Nearest Neighbors}
\newacronym{pf}{PF}{Particle Filter}
\newacronym{art}{ART}{Adaptive Resonance Theory}
\newacronym{som}{SOM}{Self-Organizing Map}
\newacronym{ae}{AE}{Autoencoder}
\newacronym{cnn}{CNN}{Convolutional Neural Network}
\newacronym{rnn}{RNN}{Recurrent Neural Network}
\newacronym{dbn}{DBN}{Deep Belief Network}
\newacronym{gan}{GAN}{Generative Adversarial Network}
\newacronym{tl}{TL}{Transfer Learning}
\newacronym{dlr}{DLR}{Deep Reinforcement Learning}
\newacronym{cep}{CEP}{Cepstral Editing Procedure}
\newacronym{pw}{PW}{Pre-Whitening }
\newacronym{lr}{LR}{Linear Regressor}
\newacronym{rf}{RF}{Random Forest}
\newacronym{ls}{LS}{Least Squares}
\newacronym{gd}{GD}{Gradient Descent}
\newacronym{sgd}{SGD}{Stochastic Gradient Descent}
\newacronym{cart}{CART}{Classification and Regression Tree}
\newacronym{mla}{MLA}{\gls{glo:mla}}
\newacronym{fa}{FA}{\gls{glo:featAg}}
\newacronym{fieldAg}{FiA}{\gls{glo:fieldagent}}
\newacronym{tn}{TN}{Transfer Learning}
\newacronym{cft}{CFT}{Continuous Fourier Transform}

\newacronym{pc}{PC}{Personal Computer} %% miscellanea
\newacronym{lcm}{LCM}{Least Common Multiple}
\newacronym{AI}{AI}{Artificial intelligence}
\newacronym{aka}{a.k.a.}{Also Known As}
\newacronym{wrt}{w.r.t.}{With Respect To}
\newacronym{pof}{POF}{Pareto Optimal Front}
\newacronym{dbscan}{DBSCAN}{Density-Based Spatial Clustering of Applications with Noise}
\newacronym{gmm}{GMM}{Gaussian Mixture Model}
\newacronym{bgmm}{BGMM}{Bayesan Gaussian Mixture Model}
\newacronym{em}{EM}{Expetaion Maximization}
\newacronym{pdf}{PDF}{Probability Density Function}
\newacronym{aic}{AIC}{Akaike Information Criterion}
\newacronym{bic}{BIC}{Bayesian Information Criterion}
\newacronym{lof}{LOF}{Local Outlier Factor}
\newacronym{rtd}{RTD}{resistance temperature detector}
\newacronym{lcsr}{LCSR}{Loop CurrentStep Response}
\newacronym{bpfo}{BPFO}{Ballpass frequency, outer race}
\newacronym{bpfi}{BPFI}{Ballpass frequency, inner race}
\newacronym{ftf}{FTF}{Fundamental train frequency (cage speed)}
\newacronym{bsf}{BSF}{Ball (roller) spin frequency}
\newacronym{mse}{MSE}{Mean Squared Error}
\newacronym{rmse}{RMSE}{Root Mean Squared Error}
\newacronym{rms}{RMS}{Root Mean Squared}
\newacronym{nasa}{NASA}{National Aeronautics and Space Administration (\gls{usa})}
\newacronym{ims}{IMS}{Center for Intelligent Maintenance Systems}
\newacronym{usa}{USA}{United States of America}
\newacronym{iso}{ISO}{International Organization for Standardization}
\newacronym{dft}{DFT}{Discrete Fourier Transform}
\newacronym{fft}{FFT}{Fast Fourier Transform}
\newacronym{wpd}{WPD}{Wavelet Packet Decomposition}
\newacronym{json}{JSON}{{\gls{glo:json}}}
\newacronym{sql}{SQL}{{\gls{glo:sql}}}
\newacronym{bson}{BSON}{Binary \gls{glo:json}}
\newacronym{cnc}{CNC}{Computer Numerical Control}
\newacronym{ie}{i.e.}{\quoted{id est} (that is)}
\newacronym{adc}{ADC}{Analog to Digital Converter}
\newacronym{csv}{CSV}{Comma Separated Values}
\newacronym{cli}{CLI}{Command Line Interface}
\newacronym{hal}{HAL}{Hardware Abstraction Library}
\newacronym{ide}{IDE}{Integrated Development Environment}
\newacronym{dma}{DMA}{Direct Memory Access}
\newacronym{gpio}{GPIO}{General Purpose Input Output}
\newacronym{anova}{ANOVA}{Analysis of Variance}
\newacronym{gui}{GUI}{Graphical User Interface}
\newacronym{wt}{WT}{Wavelet Transform}



%Symbols
\glsxtrnewsymbol[
    description={\textbf{Cluster} A set of objects that are more similar to each other than to those in other clusters.}]
    {sym:cluster}
    {\ensuremath{\vect{\mathcal{C}}}}

\glsxtrnewsymbol[
    description={\textbf{Snapshot} A set of features that describe the state of a system at a given time.}]
    {sym:snap}
    {\ensuremath{\vect{\mathcal{S}}}}
    
\glsxtrnewsymbol[
    description={\textbf{Snapshots Set} A set of snapshots \gls{sym:snap}.}]
    {sym:snapset}
    {\ensuremath{\vect{\mathbf{S}}}}

\glsxtrnewsymbol[
    description={\textbf{Distance} Vector difference between two points in the features space.}]
    {sym:dist}
    {\ensuremath{\vect{d}}}

\glsxtrnewsymbol[
    description={\textbf{Radius} Euclidean distance between the centroid \gls{sym:cent} of a cluster and its farthest point.}]
    {sym:radius}
    {\ensuremath{\vect{r}}}

\glsxtrnewsymbol[
    description={\textbf{Centroid} Point in the features space that represents a cluster. Ideally it is the center of mass of the cluster it represents.}]  
    {sym:cent}
    {\ensuremath{\vect{c}}}

\glsxtrnewsymbol[
    description={\textbf{Features} A set of metrics that describe the state of a system.}]
    {sym:feat}
    {\ensuremath{\vect{f}}}

\glsxtrnewsymbol[
    description={\textbf{Feature number} The number of features that describe the state of a system.}]
    {sym:feats}
    {\ensuremath{F}}

\glsxtrnewsymbol[
    description={\textbf{Expected value} the arithmetic mean of the possible values a random variable can take, weighted by the probability of those outcomes}]
    {sym:E}
    {\ensuremath{\E}}




%Glossary
\newglossaryentry{glo:std}{
    name={standardized},
    description={a signal that has been translated and scaled in order to have a zero mean and unit variance. It is commonly used in machine learning to ease the convergence of the algorithms.}}

\newglossaryentry{glo:snap}{
    name={snapshot},
    description={an array of features that describe the state of a system in a specific time period. It's filled with any metric (time domain, frequency domain, etc.)}}

\newglossaryentry{glo:heuristic}{
    name={heuristic},
    description={is the adjective defining a procedure that has not been proven to provide the correct solution, but that is used because of the belief that the result is useful. Heuristics are implemented into systems in the expectation that some metric would be improved. \cite{romanycia1985heuristic}}}

\newglossaryentry{glo:python}{
    name={python},
    description={ Python is a high-level programming language. It is interpreted, so it is executed line-by-line without a previous conversion in machine code. The dynamic semantics make this language suitable for rapid development of prototype application. It is also popular for writing data processing scripts. It is a mainstream language for machine learning and data science application. \cite{python}}}

\newglossaryentry{glo:cent}{
    name={centroid},
    description={The center of a cluster. It's the point that minimizes the sum of the distances between itself and all the points in the cluster. From a physical point of view, it's the center of mass of the cluster, if all the points of the cluster are treated as equal point masses.}}

\newglossaryentry{glo:edge}{
    name={edge computing},
    description={{Among the computing paradigms, edge is referred to using the data directly in the device that generated it. This avoids the transmission of large volumes of data and improves the real time response to inputs. }\cite{edge_computing_accenture}}}

\newglossaryentry{glo:clust}{
    name={cluster},
    description={In a set of data points, a cluster is a subset of the former that are more similar to each other than to the rest of the data points. This is a broad definition that leaves to the algorithm applied to perform the clustering the freedom to define what \quoted{similar} means.}}

\newglossaryentry{glo:lin-sep}{
    name={linearly separable},
    description={Consider two sets of points in an $n$-dimensional space. The data are called linearly separable if there is an ($n-1$)-dimensional hyperplane such that for every couple of points belonging to different sets, the straight segment that connects them, intersects the hyperplane. In other words, a hyperplane that separates the sets exists. \cite{lazar2009linearly}}}

\newglossaryentry{glo:likelihood}{
    name={likelihood function},
    description={The likelihood function quantifies the probability that the observed data would be generated by a specific parametric model. In other words, it is the probability of the observed data given the model parameters, and it is used to measure how well the already given parameters describe the experimental data.}}

\newglossaryentry{glo:preventivemaintenance}{
    name={Preventive Maintenance},
    description={A broad classification of maintenance tech that includes all the cases in which the maintenance action is performed before a malfunction degrades the system functionality. It aims to reduce the probability of malfunctions and failures. \cite{EN13306:2018}}
}

\newglossaryentry{glo:predeterminedmaintenance}{
    name={Predetermined Maintenance},
    description={Preventive maintenance carried out at established intervals of time or number of units of use, without previous condition investigation. \emph{Note: Intervals of times or number of unit of use may be established from knowledge of the failure mechanisms of the item\cite{EN13306:2018}.}}
}

\newglossaryentry{glo:conditionbasedmaintenance}{
    name={Condition Based Maintenance},
    description={A branch of Preventive Maintenance based on a scheduled or cyclic check of the characteristics and parameters of the maintained system, inspections and testing.  \cite{EN13306:2018} }
}

\newglossaryentry{glo:predictivemaintenance}{
    name={Predictive Maintenance},
    description={ is a Condition-based maintenance technique that aims to forecast the degradation evolution of the maintained system. It can either exploit known models or be based on repeated analysis of the device. \cite{EN13306:2018}}
}

\newglossaryentry{glo:correctivemaintenance}{
    name={Corrective Maintenance},
    description={Maintenance performed to restore the conditions of a system, after that a fault compromised its working capability. \cite{EN13306:2018}}
}

\newglossaryentry{glo:deferredcorrectivemaintenance}{
    name={Deferred Corrective Maintenance},
    description={Corrective maintenance not immediately carried out after fault detection but is delayed in accordance with given rules \cite{EN13306:2018}.}
}

\newglossaryentry{glo:immediatecorrectivemaintenance}{
    name={Immediate Corrective Maintenance},
    description={Corrective maintenance carried out without delay after a fault has been detected to avoid unacceptable consequences \cite{EN13306:2018}.}
}

\newglossaryentry{glo:scheduledmaintenance}{
    name={Scheduled Maintenance},
    description={Maintenance carried out in accordance with an established time schedule or established number of units of use. \emph{Note: Corrective deferred maintenance may also be scheduled \cite{EN13306:2018}.} }
}

\newglossaryentry{glo:remotemaintenance}{
    name={Remote Maintenance},
    description={Maintenance of an item carried out without physical access by personnel to the item \cite{EN13306:2018}.}
}

\newglossaryentry{glo:onlinemaintenance}{
    name={On Line Maintenance},
    description={A maintenance action performed during the normal operation of the device without effect on performances. \cite{EN13306:2018}}
}

\newglossaryentry{glo:onistemaintenance}{
    name={On Site Maintenance},
    description={A maintenance action performed without relocating the device into a different location. \cite{EN13306:2018}}
}

\newglossaryentry{glo:operatormaintenance}{
    name={Operator Maintenance},
    description={Maintenance actions carried out by an operator. \emph{Note: Such maintenance actions should be clearly defined.} \cite{EN13306:2018}}
}

\newglossaryentry{glo:maintenancelevel}{
    name={Maintenance Level},
    description={Level of maintenance. M \cite{EN13306:2018}.aintenance task categorization by complexity \cite{EN13306:2018}.}
}

\newglossaryentry{glo:deep}{
    name={Deep Learning},
    description={A brunch of Artificial Intelligence based on Neural Networks specialized for unstructured data. Common  inputs are texts, images, videos and audio.  \cite{KOTU2019307}}
}

\newglossaryentry{glo:trad_ml}{
    name={Traditional \gls{ml}},
    description={Any machine learning technique that is not based on neural networks.}
}
    
\newglossaryentry{glo:rul}{
    name={Remaining Useful Life},
    description={The remaining time before the degradation of a system becomes unacceptable according to a certain criterion. \cite{ISO13381_1}}
}

\newglossaryentry{glo:hyperparameter}{
    name={hyperparameter},
    description={An hyperparameter is an input of a Machine Learning algorithm that influences the model generated by the algorithm during the training. It is a parameter because it is supposed to be set before the training and remaining constant afterwards.  \citepage{hands-on-geron2022}{30}}
}

\newglossaryentry{glo:feature}{
    name={feature},
    description={a feature is a single measurable property of an object. In the context of machine learning, a feature is the result of the elaboration of input data into a new atomic quantity that describes a characteristic of the original data.}
}

\newglossaryentry{glo:polling}{
    name={polling},
    description={to cyclically collect data from a device.}
}

\newglossaryentry{glo:json}{
    name={JavaScript Object Notation},
    description={JSON is an open-standard format that uses nested attribute-value pairs and array structure. It is based on plain text and the formatting makes it easily readable by humans \cite{json_definition}.}
}

\newglossaryentry{glo:nosql}{
    name={NoSQL},
    description={A database management technique that structures the data in a form different from tables, such as key-value pairs, arrays and documents. The peculiar benefits of this practice are enhanced flexibility and scalability. \cite{noSQL_definition}}
}

\newglossaryentry{glo:sql}{
    name={Structured Query Language},
    description={a domain-specific language for managing and querying relational databases, utilizing tables to organize and structure data, facilitating efficient data retrieval, insertion, and modification operations.}
}

\newglossaryentry{glo:commissioning}{
    name={commissioning},
    description={to put a new system into working conditions.}
}

\newglossaryentry{glo:frmwrk}{
    name={framework},
    description={a framework is a structure intended to guide the development and expansion of a system. \cite{framework_definition}. In software development, a framework is a set of functions, classes and practices that can be recalled to develop a solution to a problem.}
}

\newglossaryentry{glo:fieldagent}{
    name={Field Agent},
    description={a software agent that polls the data from the field and stores them in a database in a suitable formatted way.}
}

\newglossaryentry{glo:featAg}{
    name={Feature Agent},
    description={a software agent that extracts the features from the data polled by the \gls{glo:fieldagent} and stores them in a database in a suitable formatted way.}
}

\newglossaryentry{glo:mla}{
    name={Machine Learning Agent},
    description={software agent that trains the models, evaluates the metrics on new data, and makes predictions about the future evolution of the metrics. It also interfaces itself with the operator.}
}

\newglossaryentry{glo:mongodb}{
    name={MongoDB},
    description={a source-available, cross-platform, document-oriented database program. }
}

\newglossaryentry{glo:pickle}{
    name={Pickle format},
    description={A Python module that enables the conversion of an object into a byte stream. This process (Pickling) is also called serialization. The inverse operation is also available in this module and it reconstructs the original object from a byte stream. This is used to save an object (and its current configuration) into a file and retrieve it when necessary. \cite{python_docs}}
}

\newglossaryentry{glo:agent}{
    name={agent},
    description={{a computer application that performs tasks continuously and autonomously. For example, a softeare agent may serve the purpose of continuously checking for duplicate files in a certain directory and removing the duplicates. This simple example is non-exhaustive as the tasks performed by agents may be complex.} \cite{software_agent}}
}

\newglossaryentry{glo:leadtime}{
    name={Lead Time},
    description={The interval between the detection of a novelty, and a malfunction happening.}
}

\newglossaryentry{glo:sklearn}{
    name={\texttt{sklearn}},
    description={Scikit-learn is a free Python-based machine learning library. It is commonly used for classification, regression, and clustering tasks. It implements algorithms such as support vector machines, gaussian mixtures, random forests, k-means, DBSCAN and many others. The library integrates with most of Python's numerical libraries.}
}